### 2019-12-02 Papers/Torque_Abstract/main.tex
made reference file shared between the different papers
added section on model uncertainties

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[parfill]{parskip}  % no indents
\usepackage{geometry}
 \geometry{
 a4paper,
 left=25mm,
 top=40mm,
 right=25mm,
 bottom=27mm
 }
\usepackage{natbib}  % references
\usepackage{graphicx}  % plots
\usepackage{scrextend}  % indent authors
\usepackage{amsmath}  % math typesetting
\usepackage{graphicx}
\usepackage{subcaption}

% typeset in sans serif to match the prompt
\usepackage{lmodern}
\renewcommand{\familydefault}{\sfdefault}
% correct the section heading size
\usepackage{titlesec}
\titleformat*{\section}{\normalsize\bfseries}

@@

% =============================================
\section{Methodology}
To compute parameter sensitivities we use a global sensitivity analysis based on the Sobol expansion approach, which decomposes the total variance of the quantity of interest (model output) into contributions from individual parameters and their combinations, similar to \cite{Echeverria2017,Murcia2018,Rinker2016}. We employ the uncertainty quantification toolbox \texttt{UQLab} \cite{uqlab}, which computes the Sobol indices from a sparse polynomial chaos expansion. \texttt{UQLab}'s modular structure allows for easy integration with available BEM codes.

The geometric uncertainties currently considered are chord and twist distribution, whereas the model uncertainty enters via uncertainty in lift- and drag-polars. In order to express the chord, twist, lift and drag distributions along the turbine blade, an efficient parameterization is needed that gives flexible control over the prescribed uncertainty while limit the number of required parameters. We have chosen to use Non-Uniform Rational Basis Splines (NURBS) for this purpose, similar to \cite{Echeverria2017}.

% =============================================
\section{Results}
The aeroelastic code that we use is the \texttt{ECN Aero-Module} \cite{Boorsma2012} and the turbine is the 2MW NM80 turbine from the DANAERO project \cite{Troldborg2013} with a blade radius of 38.8m. The data for lift ($Cl$) and drag ($Cd$) polars are available at four locations along the blade radius at 11.87m, 17.82m, 28.97m and 35.53m. The reference value of polars are obtained from wind-tunnel experiment with 3D corrections. Random samples of chord, twist, lift- and drag-polars are obtained by perturbing the control points with a uniformly distributed random variable. For chord and twist, we independently perturb control points at different locations as shown in Fig. \ref{fig:samples} (a) - (b). For $Cl$ and $Cd$, all control points are perturbed using a same random number.

In Fig. \ref{fig:Sobol}, we show the total order Sobol indices as a measure of sensitivity for different geometric and model parameters on power production. The control points are named

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.4\linewidth}
    \includegraphics[width=\linewidth]{Chord_samples_torque.eps}
   % \caption{Coffee.}
  \end{subfigure}
  \begin{subfigure}[b]{0.4\linewidth}
    \includegraphics[width=\linewidth]{Twist_samples_torque.eps}
   % \caption{More coffee.}
  \end{subfigure}

  \begin{subfigure}[b]{0.4\linewidth}
    \includegraphics[width=\linewidth]{Cl_samples_torque.eps}
    %\caption{Coffee.}
  \end{subfigure}
  \begin{subfigure}[b]{0.4\linewidth}
    \includegraphics[width=\linewidth]{Cd_samples_torque}
    %\caption{More coffee.}
  \end{subfigure}
  \caption{Random realization of twist, chord, lift- and drag-polars.}
  \label{fig:samples}
\end{figure}
\begin{figure}[h!]
  \centering
    \includegraphics[width=\linewidth]{SA_Power_Chord_Twist_CD_CL_torque.eps}
  \caption{Total order Sobol indices for the sensitivity analysis of geometrical and model parameters.}
   \label{fig:Sobol}
\end{figure}
% =============================================
\section{Conclusions}
Global sensitivity analysis is a powerful tool to identify important input parameters associated with aeroelastic models. Sobol indices computed using sparse polynomial expansion is very efficient and can be used to analyze large number of input parameters. In the full paper, we will present a sensitivity assessment with a more model parameters.
% =============================================
\bibliographystyle{plain}
\bibliography{references,Mendeley_refs}

>>>>

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[parfill]{parskip} % no indents
\usepackage{geometry}
 \geometry{
 a4paper,
 left=25mm,
 top=40mm,
 right=25mm,
 bottom=27mm
 }
\usepackage{natbib} % references
\usepackage{graphicx} % plots
\usepackage{scrextend} % indent authors
\usepackage{amsmath} % math typesetting
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{microtype}
% typeset in sans serif to match the prompt
\usepackage{lmodern}
\renewcommand{\familydefault}{\sfdefault}
% correct the section heading size
\usepackage{titlesec}
\titleformat*{\section}{\normalsize\bfseries}

@@

% =============================================
\section{Methodology}
To compute parameter sensitivities we use a global sensitivity analysis (GSA) based on the Sobol expansion approach, which decomposes the total variance of the quantity of interest (model output) into contributions from individual parameters and their combinations, similar to \cite{Echeverria2017,Rinker2016}. We employ the uncertainty quantification toolbox \texttt{UQLab} \cite{uqlab}, which computes the Sobol indices from a sparse polynomial chaos expansion. \texttt{UQLab}'s modular structure allows for easy integration with available BEM codes.

The geometric uncertainties currently considered are chord and twist distribution, whereas the model uncertainty enters via uncertainty in lift- and drag-polars. To express the chord, twist, lift and drag distributions along the turbine blade, an efficient parameterization is needed that gives flexible control over the prescribed uncertainty while limiting the number of required parameters. We have chosen to use Non-Uniform Rational Basis Splines (NURBS) for this purpose, similar to \cite{Echeverria2017}.

% =============================================
\section{Results}
The aeroelastic code that we use is the \texttt{ECN Aero-Module} \cite{Boorsma2012} and the turbine is the 2MW NM80 turbine (blade radius of 38.8m) from the DANAERO project \cite{Troldborg2013}. The data for airfoil lift- and drag-polars are available at four locations along the blade at 11.87m, 17.82m, 28.97m and 35.53m. %The reference value of polars are obtained from wind-tunnel experiment with 3D corrections. 
The lift variables are numbered from Cl1 - Cl4 and drag from Cd1 - Cd4 along the blade radius. Random samples of chord, twist, lift- and drag-polars are obtained by perturbing the control points with a uniformly distributed random number.  Each of the control points for chord (Ch1 - Ch5) and twist (Tw1 - Tw6)  are perturbed independently. Thus, by locally perturbing the chord and twist curves, we can identify locations along the blade that are sensitive to turbine response. For a given lift and drag curve, all control points are perturbed (globally) using the same random number. Here, we are interested in knowing at what locations the inaccuracies in polars may lead to the most variations in the turbine output. Random samples for these input parameters are presented in Fig. \ref{fig:samples}. In Fig. \ref{fig:Sobol}, we show the total order Sobol indices as a measure of sensitivity for different geometric and model parameters on the power output. We observe that the model parameters are relatively more sensitive than the geometric parameters. Within geometric parameters, chord distribution shows a significantly higher sensitivity compared to the twist variables.
\begin{figure}[h!]
 \centering
 \includegraphics[trim={0 1.6cm 0 0},clip, scale=0.65]{figure1.pdf}
 \caption{Random realization of chord, twist, lift- (Cl2) and drag-polars (Cd2).}
 \label{fig:samples}
\end{figure}
\begin{figure}[h!]
 \centering
  \includegraphics[width=\linewidth]{SA_Power_chord_twist_Cl_Cd.eps}
 \caption{Total order Sobol indices for the sensitivity analysis of geometrical and model parameters.}
  \label{fig:Sobol}
\end{figure}
% =============================================
\section{Conclusions}
We have shown that Sobol indices computed using sparse polynomial expansion is highly suitable for high-dimensional GSA. In the full paper, we will present a detailed sensitivity assessment that will include more model parameters. The identified sensitive parameters will further be utilized to develop calibrated BEM models.
% =============================================
\bibliographystyle{plain}
\bibliography{../references,../Mendeley_refs}
